---
title: "Plots in Supplementary Material"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages

Install the `reliabilitydiag` package located in the root directory.
The `here` package identifies that directory by the location of the replication_DGJ20.Rproj file.

```{r eval = FALSE}
library(here)
devtools::install_local(here("reliabilitydiag_0.1.0.tar.gz"))
library(reliabilitydiag)
```

### Required packages and compilation environment

```{r message = FALSE}
library(here)
library(reliabilitydiag)
library(doParallel)
library(dplyr)
library(rlist)
library(purrr)
library(EnvStats)
library(ggplot2)
library(RColorBrewer)
library(ggExtra)
library(gridExtra)

sessionInfo()
```


## Section S1: Experimental data sets

### Plots for Fig S1

```{r DGPs_DataDriven, message=FALSE, warning=FALSE, fig.width = 20, fig.height = 5, fig.keep = 1:3}
source("DGPs_DataDriven.R", local = knitr::knit_global())
```

```{r DGPs_DataDriven2, fig.width = 15, fig.height = 10}
gridExtra::grid.arrange(p.SPF)
```


## Section S2: (In)stability: Illustrative examples

### Plots for Fig S2--S5

```{r Instabilities_QBinning, message = FALSE, fig.width = 20, fig.height = 20}
source("Instabilities_QBinning.R", local = knitr::knit_global())
```


## Section S4: Uncertainty quantification: Data driven simulations

### Coverage simulations

The following source file performs an extensive simulation of the coverage
for the uncertainty quantification options: consistency, confidence.

**Note:** Multiple hours of runtime. Only run if necessary to confirm reproducibility.

```{r sim_coverage, eval = FALSE}
source("sim_Coverage_Bands_DataDriven.R", local = knitr::knit_global())
```


### Plots for Fig S6--S9

```{r fig_coverage, message = FALSE, fig.width = 15, fig.height = 15}
source("fig_coverage.R", local = knitr::knit_global())
```


## Section S5: Statistical efficiency of CORP: Data driven simulations

### Efficiency simulations

The following source file performs an extensive simulation of the CORP efficiency
in comparison to various binning and counting approaches.

**Note:** Multiple hours of runtime. Only run if necessary to confirm reproducibility.

```{r sim_efficiency, eval = FALSE}
source("sim_Efficiency_DataDriven.R", local = knitr::knit_global())
```


### Plots for Fig S10--S13

```{r fig_efficiency, message = FALSE, fig.width = 15, fig.height = 15}
source("fig_efficiency.R", local = knitr::knit_global())
```


## Section S6: CORP discrimination diagrams

### Plots for Fig S14

```{r discrimination_diagrams, message = FALSE, fig.width = 20, fig.height = 5}
source("discrimination_diagrams.R", local = knitr::knit_global())
```

