---
title: "Plots in Main Article"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages

Install the `reliabilitydiag` package located in the root directory.
The `here` package identifies that directory by the location of the replication_DGJ20.Rproj file.

```{r eval = FALSE}
library(here)
devtools::install_local(here("reliabilitydiag_0.1.0.tar.gz"))
library(reliabilitydiag)
```

### Required packages and compilation environment

```{r message = FALSE}
library(here)
library(dplyr)
library(tidyr)
library(reliabilitydiag)
library(RColorBrewer)
library(ggplot2)

library(rlist)
library(tibble)
library(EnvStats)
library(ggplot2)
library(dplyr)
library(doParallel)
library(RColorBrewer)
library(reshape2)
library(devtools)
library(ggExtra)
library(gridExtra)

sessionInfo()

```


## Section "Reliability diagrams: Binning and Counting"

### Required CRAN packages

- here
- reliabilitydiag
- dplyr
- purrr
- ggplot2
- gridExtra

### Plots for Fig 1

```{r Fig1, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 15}
source("Fig1.R", local = knitr::knit_global())
```

### Plots for Fig 2

```{r Fig2, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 10}
source("Fig2.R", local = knitr::knit_global())
```


## Section "Uncertainty quantification"

### Required CRAN packages

- here
- reliabilitydiag
- dplyr
- purrr
- ggplot2
- gridExtra
- doParallel

### Plots for Fig 3

```{r Fig3, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 10}
source("Fig3.R", local = knitr::knit_global())
```

### Plots for Fig 4

The simulations are only rerun when the `runSimulations` variable in
`"sim_Coverage_Bands_MainArticle.R"` is `TRUE`.

```{r Fig4, message=FALSE, warning=FALSE, fig.width = 14, fig.height = 8}
source("sim_Coverage_Bands_MainArticle.R", local = knitr::knit_global())
```

## Section "Discussion"

### Required CRAN packages

- here
- reliabilitydiag
- dplyr
- purrr
- ggplot2
- gridExtra
- ggExtra

### Plots for Fig 5

```{r Fig5, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 5}
source("Fig5.R", local = knitr::knit_global())
```

## Appendix B "Statistical Efficiency of CORP"

### Required CRAN packages

- doParallel
- dplyr
- tibble
- ggplot2
- reliabilitydiag
- RColorBrewer


### Plots for Fig 6

The simulations are only rerun when the `runSimulations` variable in
`"sim_Efficiency_MainArticle.R"` is `TRUE`.

```{r Fig6, message=FALSE, warning=FALSE, fig.width = 14, fig.height = 8}
source("sim_Efficiency_MainArticle.R", local = knitr::knit_global())
```


