---
title: "Plots in Main Article"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages

Install the `reliabilitydiag` package located in the root directory.
The `here` package identifies that directory by the location of the replication_DGJ20.Rproj file.

```{r eval = FALSE}
library(here)
devtools::install_local(here("reliabilitydiag_0.1.0.tar.gz"))
library(reliabilitydiag)
```

### Required packages and compilation environment

```{r message = FALSE}
library(here)
library(reliabilitydiag)
library(dplyr)
library(doParallel)
library(ggplot2)
library(RColorBrewer)
library(purrr)
library(gridExtra)
library(ggExtra)

sessionInfo()

```


## Section "Reliability diagrams: Binning and Counting"

### Plots for Fig 1

```{r Fig1, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 15}
source("Fig1_miscalibration.R", local = knitr::knit_global())
```

### Plots for Fig 2

```{r Fig2, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 10}
source("Fig2_instability.R", local = knitr::knit_global())
```


## Section "Uncertainty quantification"

### Plots for Fig 3

```{r Fig3, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 10}
source("Fig3_uncertainty_quantification.R", local = knitr::knit_global())
```

### Simulations for Fig 4

The following source file performs an extensive simulation of the coverage
for the uncertainty quantification options: consistency, confidence.

**Note:** Multiple hours of runtime. Only run if necessary to confirm reproducibility.

```{r sim_coverage, eval = FALSE}
source("sim_Coverage_Bands_MainArticle.R", local = knitr::knit_global())
```

### Plots for Fig 4

```{r Fig4, message=FALSE, warning=FALSE, fig.width = 14, fig.height = 8}
source("Fig4_coverage.R", local = knitr::knit_global())
```

## Section "Discussion"

### Plots for Fig 5

```{r Fig5, message=FALSE, warning=FALSE, fig.width = 10, fig.height = 5}
source("Fig5_discrimination.R", local = knitr::knit_global())
```

## Appendix B "Statistical Efficiency of CORP"

### Simulations for Fig 6

The following source file performs an extensive simulation of the CORP efficiency
in comparison to various binning and counting approaches.

**Note:** Multiple hours of runtime. Only run if necessary to confirm reproducibility.

```{r sim_efficiency, eval = FALSE}
source("sim_Efficiency_MainArticle.R", local = knitr::knit_global())
```

### Plots for Fig 6

```{r Fig6, message=FALSE, warning=FALSE, fig.width = 14, fig.height = 8}
source("Fig6_efficiency.R", local = knitr::knit_global())
```
